Placeholder Title... Something About Delegating Quantum Computations

### 2019-11-21 preliminaries.tex
Add TODO for de Finetti
Change TODOs to note macros
Add SampBQP

@@

>>>>

We define $\SampBQP$ the same way as from \cite{aaronson_2013}.

\begin{definition}
	A sampling problem $S$ is a collection of probability distributions $(D_x)$, one for each input string $x\in\set{0,1}^n$, where $D_x$ is a distribution over $\set{0,1}^{p(n)}$ for some fixed polynomial $p$.
\end{definition}

\begin{definition}
	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which there exists a polynomial-time quantum algorithm that, given $x$ as input, samples from from a probability distribution $C_x$ such that $\norm{C_x-D_x}<\varepsilon$.
\end{definition}

@@

\Ethan{Explain the terminologies. Also check do something about the integral vs weighted sum}
